\propertitle

### 2020-03-16 replies1_ncomp.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T22:02:36+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different probabilities
on the data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant, from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.

@@

Third, \emph{the evidence $\p(D \| M_{i})$ for a model automatically takes
  care of its complexity}. This happens because the probability over the
data space is normalized. If $M_{2}$ has a typical-data volume larger than
$M_{1}$'s, then it must also assign lower probability to each volume
element therein, to ensure normalization. As a result, if the observed data
$D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{1}) > \pf(D^{*} \| M_{2})$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the observed data are for each model and each
model's power. This is the so-called automatic Ockham razor of Bayes's
theorem, extensively explained by MacKay
\citey{mackay1992}[also][\sect~28.1]{mackay1995_r2003}. And this is the
reason why we are personally satisfied with simply comparing the evidence
for any two models.

In our calculations, however, we are using a zeroth-order Laplace
approximation for calculating the evidence in \sect~4. A first-order
approximation (containing the width of the distribution, influenced by the
typical-set volume above) would correct for the model's power. We believe
that the correction would nevertheless be the same in the calculations
based on the larger population, \eqns~(11), and on the sample, \eqns~(12).
Hence the difference in the two approaches -- our main message -- should
persist. But it would be better to check this.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-03-16T22:12:34+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourtrue% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimfalse
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\firstdraft}{16 March 2020}
\newcommand*{\firstpublished}{16 March 2020}
\newcommand*{\updated}{\ifarxiv***\else\today\fi}
\newcommand*{\propertitle}{Sketch of replies to N. Comp. reviews%\\{\large ***}%
}% title uses LARGE; set Large for smaller
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{}
\newcommand*{\pdfauthor}{}
\newcommand*{\headauthor}{}
\newcommand*{\reporthead}{}%\ifarxiv\else Open Science Framework \href{https://doi.org/10.31219/osf.io/***}{\textsc{doi}:10.31219/osf.io/***}\fi}% Report number

@@

First, two models are different if they have the same family but different
distributions over it. In fact they clearly lead to different probabilities
on the data space. Two such models are also mutually exclusive,
$\p(M_{1} \land M_{2} \|I)=0$, because we cannot use $M_{1}$'s family
distribution \emph{and} $M_{2}$'s family distribution at the same time.
It's either-or. This consequence makes sense from a nonparametric
perspective, where a parametric model is just a delta-like nonparametric
distribution, concentrated on a lower-dimensional manifold (the family
above) of the full space of distributions \citep[p.~761]{draperetal1996}.
The notion of nested models becomes unimportant from this perspective.
Some authors try to define some \enquote{standard} distribution associated
to a family, but we agree with those \citep[\eg][]{copasetal1979}[DeGroot
in][]{lindleyetal1982} who find such definitions ultimately arbitrary. Many
such distributions lead, moreover, to mathematical singularities.

@@

Third, \emph{the evidence $\p(D \| M_{i})$ for a model automatically takes
  care of its complexity}. This happens because the probability over the
data space is normalized. If the more powerful $M_{2}$ has a typical-data
volume larger than $M_{1}$'s, then it must also assign lower probability to
each volume element therein, to ensure normalization. As a result, if the
observed data $D^{*}$ lie in the typical volumes of both models, then
$\pf(D^{*} \| M_{2}) < \pf(D^{*} \| M_{1})$: \emph{the evidence is
  automatically penalizing the larger model}. There is a continuous
trade-off between how typical the observed data are for each model and each
model's power. This is the so-called automatic Ockham razor of Bayes's
theorem, extensively explained by MacKay
\citey{mackay1992}[also][\sect~28.1]{mackay1995_r2003}. And this is the
reason why we are personally satisfied with simply comparing the evidence
for any two models.

In our calculations, however, we are using a zeroth-order Laplace
approximation for calculating the evidence in \sect~4. A first-order
approximation (containing the width of the distribution, influenced by the
typical-set volume above) would correct for the model's power
\citep[\sect~2.2]{mackay1992}. We believe that the correction would
nevertheless be the same in the calculations based on the larger
population, \eqns~(11), and on the sample, \eqns~(12). Hence the difference
in the two approaches -- our main message -- should persist. But it would
be better to check this.
